Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-11-24 Scripts/Initial_Analysis.Rmd
FIxed top 5 ssr map

SummaryProp <- function(taxon_key,links="NA"){

@@

EEZProp <- function(taxon_list,links="NA"){

  spp <- bind_rows(
    lapply(taxon_list,SummaryProp,links)
  )

@@

PropChange <- function(taxon_list,links="NA"){

  eez <- EEZProp(taxon_list,links)

@@

###  Year of Eergence Analysis

@@

@@

@@

##### Fig. 3 Mapping the time of emergence

###### Mean ToE and vulnerabillity Index

# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid,sau_fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
  ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  # filter(metric != "n_taxa") %>% 
  mutate(
    reverse = abs(value-2100)  + 2000
  )

@@

# grey_eez <- World_eez_sf %>% 
#   filter(!eezid %in% Eez_d_hist$eezid,
#          !eez_name %in% Neighbours$eez_name)

# -------------------------- #
# Call plot for both tresholds
# -------------------------- #
tresh_list <- c("tresh_one","tresh_two")
for(i in 1:2){

@@

Note this chunk needs the previous one to be ran up to the for-loop

@@

# Grey land
grey_land <- World_map %>% 
  # filter(is.na(fishing_entity_id)) %>% 
  filter(!sovereignt %in% c("Antarctica"))

# Inlcude the participation of species

#   geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
#   geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +

eez_map <- ggplot(toe_map_data) +
  geom_sf(aes(fill = value), # for 2000 to 2100),
          color =  "white",
          size = 0.1
  ) +
  geom_sf(data = grey_land, aes(),
          fill = "grey50", 
          color =  "white",
          size = 0.1) +
  geom_sf(data = no_toe_eez, aes(fill = as.numeric(value)),
          color =  "white",
          size = 0.1) +
  scale_fill_viridis("Average year of range shift",
                     limits = c(2000,2100),
                     breaks = seq(2000,2100,25),
                     labels = seq(2000,2100,25),
                     direction = -1,
                     na.value = "lightblue"
  ) +
  my_ggtheme_m(leg_pos = "bottom") +
  theme(legend.key.width = unit(3, "line")) +
  guides(
    fill=guide_colorbar(title.position="top", 
                        title.hjust =0.5)
  )

land_map <- ggplot() +
  geom_sf(data = World_map_part,
          aes(fill = participation-2000, 
              color = participation-2000),
          size = 0.1
  )  +
  geom_sf(data = no_toe_land, aes(fill = as.numeric(value),
                                  color = as.numeric(value)),
          size = 0.1) +
  scale_fill_viridis("Transboundary fish revenue (%)",
                     limits = c(0,100),
                     breaks = seq(0,100,25),
                     labels = seq(0,100,25),
                     direction = 1,
                     na.value = "lightblue",
                     option = "A"
  ) +
  scale_color_viridis("Transboundary fish revenue (%)",
                      limits = c(0,100),
                      breaks = seq(0,100,25),
                      labels = seq(0,100,25),
                      direction = 1,
                      na.value = "lightblue",
                      option = "A"
  ) +
  my_ggtheme_m(leg_pos = "bottom") +
  theme(legend.key.width = unit(3, "line")) +
  guides(
    fill=guide_colorbar(title.position="top",
                        title.hjust =0.5)
  )

# ggsave(
#   plot = land_map,
#   width = 8,
#   height = 6,
#   units = "in",
#   filename = "./Figures/eez_map_supp.png"
# )

@@

ggplot() +
  geom_sf(data = rnaturalearth::ne_countries(scale = 'large', returnclass = c("sf")),aes())

@@

##### Fig. 4 Mapping the time of emergence Of Top stocks

@@

top_stocks_per_country <- Eme_Res %>% 
  rename(geo_region = un_sub_region) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,geo_region,tresh,taxon_key) %>% 
  summarise(n()) %>% 
  left_join(Sau_data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  filter(!is.na(variable)) %>% 
  group_by(sau_fishing_entity,geo_region,tresh,variable) %>% 
  # Select top 5 most valuable stocks
  top_n(5,value) %>% 
  left_join(Exploited_spp_list)

@@

### Species level analysis

#### Fig. 5 Species Boxplot

@@

Dem_pel <- Eme_Res %>% 
  filter(tresh == selected_tresh,
         !is.na(un_sub_region)) %>% 
  left_join(Spp_env_pref) %>% 
  mutate(DemersPelag = ifelse(is.na(DemersPelag),"other",paste(DemersPelag)
                              #                             ifelse(DemersPelag %in% c("bathypelagic","benthopelagic"), "bathy-bentho-pelagic",paste(DemersPelag)
                              #                             )
  ),
  un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and the Car.",paste(un_sub_region)))

@@

# ------------------- #
# Test normal asumptions 
# ------------------- #

hist(Stats_data$emerging_yr) # Positevely skewed
qqnorm(Stats_data$emerging_yr) # not normally distributed
skewness(Stats_data$emerging_yr) #1.02
kurtosis(Stats_data$emerging_yr) #2.82

@@

# Multiple differences but Eastern Asia, Lat. Ame. Car. and Polinesia are the nes who differe the most (e.g. differe with more revions).

@@

##  Prooportion Analysis

@@

```{r fig5_paths, eval = T, echo = T}

# A function that makes a dateframe per connection (we will use these connections to plot each lines)
data_for_connection=function( dep_lon, dep_lat, arr_lon, arr_lat, group){
  inter <- gcIntermediate(c(dep_lon, dep_lat), c(arr_lon, arr_lat), n=50, addStartEnd=TRUE, breakAtDateLine=F)             
  inter=data.frame(inter)
  inter$group=NA
  diff_of_lon=abs(dep_lon) + abs(arr_lon)
  if(diff_of_lon > 180){
    inter$group[ which(inter$lon>=0)]=paste(group, "A",sep="")
    inter$group[ which(inter$lon<0)]=paste(group, "B",sep="")
  }else{
    inter$group=group
  }
  return(inter)
}
pal <- wesanderson::wes_palette("Zissou1",100,type = "continuous")

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
            # left_join(Eez_centroid_eck,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  # left_join(Eez_centroid_eck,
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na()

# Get paths data
path_data <- Data %>% 
  filter(
    variable %in% c("mean_eez")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

for(i in c(1:nrow(path_data))){
  tmp=data_for_connection(path_data$start_lon[i], path_data$start_lat[i], path_data$end_lon[i], path_data$end_lat[i] , i)
  # tmp$homecontinent=summary$homecontinent[i]
  tmp$per_early_plot=path_data$per_early_plot[i]
  tmp$per_mid_plot=path_data$per_mid_plot[i]
  tmp$source=path_data$source[i]
  tmp$objective=path_data$target[i]
  data_ready_plot=rbind(data_ready_plot,tmp)
}

@@

# SELECT A TIME STEP
# time_toplot <- "per_mid"
time_toplot <- "per_early"

# ----------------------------- #

@@

# Plot
p <-
  ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,
          col = "white") +
  geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
  geom_sf(data = subset(sf_ready_plot, percentage >= 0), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = point_data, aes(), color = "grey90") +
  geom_path(data = subset(arrows_data, percentage >= 0),
            aes(X, Y,
                group = group,
                col = percentage
            ),
            size = 1,
            arrow = arrow(length = unit(0.01, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m(leg_pos = "bottom") +
  scale_color_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(sf_ready_plot$percentage,na.rm=T)),
                        breaks = seq(0,max(sf_ready_plot$percentage,na.rm=T),10),
                        labels = c(seq(0,max(sf_ready_plot$percentage-10,na.rm=T),10),">50")
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                       colours = pal,
                       limits = c(0,max(sf_ready_plot$percentage,na.rm=T)),
                       breaks = seq(0,max(sf_ready_plot$percentage,na.rm=T),10),
                       labels = c(seq(0,max(sf_ready_plot$percentage-10,na.rm=T),10),">50")
  ) + guides(
    color=guide_colorbar(title.position="top")
  ) +
  theme(legend.key.width = unit(4,"line"))

@@

### Figure S6. Regional plots

Note that the following chunk needs the previous one to be ran

@@

# Lat_am_land <- World_map %>% 
# filter(region_wb %in% c("Latin America & Caribbean") |
# sau_fishing_entity %in% c("USA","Mexico")
# )

Lat_am_eez <- World_eez_sf %>% 
  select(sf_eez_name = eez_name,everything()) %>% 
  left_join(Matching_names) %>% 
  filter(
    un_sub_region == "Latin America and the Caribbean",
    !str_detect(sf_eez_name,"Pacific"),
    !sf_eez_name %in% c("USA (East Coast)","Suriname","Guyana","French Guiana","Bermuda (UK)","Brazil","El Salvador")
  )

Lat_am_data <- sf_ready_plot %>% 
  filter(source %in% Lat_am_eez$sf_eez_name,
         objective %in% Lat_am_eez$sf_eez_name)

Lat_am_paths <- arrows_data %>% 
  filter(source %in% Lat_am_eez$sf_eez_name,
         objective %in% Lat_am_eez$sf_eez_name)

Lat_am_points <- point_data %>% 
  filter(source %in% Lat_am_eez$sf_eez_name,
         target %in% Lat_am_eez$sf_eez_name)

Lat_am_n_taxa <- n_taxa_map %>% 
  filter(
    region_wb == "Latin America & Caribbean",
    # !str_detect(sf_eez_name,"Pacific"),
    # !sf_eez_name %in% c("USA (East Coast)","Suriname","Guyana","French Guiana","Bermuda (UK)","Brazil","El Salvador")
  )

lat_am_map <- ggplot() +
  geom_sf(data = Lat_am_eez, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(Lat_am_n_taxa, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,
          col = "white") +
  # geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
  geom_sf(data = subset(Lat_am_data, percentage >= 0), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = Lat_am_points, aes(), color = "grey90") +
  geom_path(data = subset(Lat_am_paths, percentage >= 0),
            aes(X, Y,
                group = group,
                col = percentage
            ),
            size = 1,
            arrow = arrow(length = unit(0.01, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m(leg_pos = "bottom") +
  coord_sf(xlim = c(-9000000,-5000000),ylim = c(1000000, 4000000)) + 
  labs(x = "", y = "") +
  # scale_x_continuous(breaks = seq(-100,60,10)) +
  # scale_y_continuous(breaks = seq(10,30,10)) +
  my_ggtheme_m(leg_pos = "bottom") +
  theme(
    panel.background = element_rect(fill = "white", color = "white"),
    panel.grid.major =  element_line(color = "white")
  ) +
  scale_color_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(Lat_am_data$percentage)),
                        breaks = seq(0,max(Lat_am_data$percentage),10)
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                       colours = pal,
                       limits = c(0,max(Lat_am_data$percentage)),
                       breaks = seq(0,max(Lat_am_data$percentage),10)
  ) + guides(
    color=guide_colorbar(title.position="top", 
                         title.hjust =0.5)
  ) +
  theme(legend.key.width = unit(4,"line"))

@@

EU_data <- sf_ready_plot %>% 
  filter(source %in% EU_eez$sf_eez_name)

EU_map <- ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,
          col = "white") +
  # geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
  geom_sf(data = subset(sf_ready_plot, percentage >= 0), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = point_data, aes(), color = "grey90") +
  geom_path(data = subset(arrows_data, percentage >= 0),
            aes(X, Y,
                group = group,
                col = percentage
            ),
            size = 1,
            arrow = arrow(length = unit(0.03, "npc"),
                          ends = "first"),
            show.legend = NA) +
  # my_ggtheme_m(leg_pos = "bottom") +
  coord_sf(xlim = c(-1300000,2000000),ylim = c(5500000, 7500000))  +
  labs(x = "", y = "") +
  scale_x_continuous(breaks = seq(-100,60,10)) +
  scale_y_continuous(breaks = seq(10,30,10)) +
  my_ggtheme_m(leg_pos = "bottom") +
  theme(
    panel.background = element_rect(fill = "white", color = "white"),
    panel.grid.major =  element_line(color = "white")
  ) +
  scale_color_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(EU_data$percentage)),
                        breaks = seq(0,max(EU_data$percentage),10)
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                       colours = pal,
                       limits = c(0,max(EU_data$percentage)),
                       breaks = seq(0,max(EU_data$percentage),10)
  ) + guides(
    color=guide_colorbar(title.position="top",
                         title.hjust =0.5)
  ) +
  theme(legend.key.width = unit(4,"line"))

@@

##### Fig. TOP 5

@@

top_taxon_list <-  unique(top_stocks_per_country$taxon_key)
# Read proportion results
suppressMessages(
  top_prop_results <- PropChange(top_taxon_list, links="y") %>%
    filter(!is.na(eez_neighbour)) %>%
    mutate(per_mid_plot =ifelse(per_mid >= 100, 100,
                                ifelse(per_mid <= -100,-100,per_mid)
    ),
    per_early_plot =ifelse(per_early >= 100, 100,
                           ifelse(per_early <= -100,-100,per_early)
    )
    )
)

@@

# Prepare data from results
top_data <- top_prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  # gather("variable","value",per_early:per_early_plot) %>% 
  filter(
    variable %in% c("mean_eez","n_spp")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

View(top_data)

# Convert to data to spatial
top_network_data_sf <- top_data %>%
  select(start_lon, start_lat, end_lon, end_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  # st_sfc(crs = "+proj=eck4") %>% # for tbular plot
  st_sf(geometry = .)%>%
  bind_cols(top_data) %>%
  select(everything(), geometry) %>% 
  # Set circles ('cus the world is not flat!)
  st_segmentize(units::set_units(100, km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>%
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>%
  # sf::st_sf(crs = 4326)
  sf::st_sf(crs = "+proj=eck4") # for tbular plot

#  unpack the coordinates of each feature 
coord_data <- as.data.frame( st_coordinates(st_cast(top_network_data_sf,"MULTILINESTRING")$geometry))

>>>>

# taxon_key = "600147"
# top_stocks_per_country

SummaryProp <- function(taxon_key,links="NA", top = F){

  if(top == T){
    # Reads taxon data
    proportion_data <- fread(paste(my_path("R",extra_path = "Proportion_2005c/"),"proportion_",taxon_key,".csv", sep="")) %>% 
      filter(!is.na(eez_neighbour)) %>% 
      rename(sf_eez_name = eez_name) %>% 
      left_join(Matching_names) %>% 
      semi_join(top_stocks_per_country) %>% 
      select(
      1:4,
      ensemble_mean = catch_proportion_temp_mean_ensemble_mean,
      ensemble_sd = catch_proportion_temp_mean_ensemble_sd) %>% 
      rename(eez_name = sf_eez_name)

@@

EEZProp <- function(taxon_list,links="NA",top = F){

  spp <- bind_rows(
    lapply(taxon_list,SummaryProp,links,top = top)
  )

@@

PropChange <- function(taxon_list,links="NA", top = F){

  eez <- EEZProp(taxon_list,links, top = top)

@@

###  Time of Emergence Analysis

@@

Timeline of shifts in transboundary shared stock distribution. (A) Number of stocks (cumulative) whose distribution centroids that have shifted beyond natural variations over time (from 2006 to >2100), (B) Number of EEZs (cumulative) with the distribution centroid of at least one stock that have shifted beyond natural variations and (C) proportion of total shifting stocks and EEZs with at least one stock shifting beyond natural variability. Dashed lines represent the year by which countries have committed to reach full implementation of the 2030 Agenda, as well as mid and late change in range shift (Methods), respectively.

###### Generate data needed

@@

###### Plot histograms

@@

##### Fig. 3 Mapping the time of emergence and the participation

Year of change in the shared distribution of 4,119 transboundary stocks. A) Land polygons show the contribution of shifting stocks to a country or territory’s total fishing revenue from transboundary stocks. Exclusive Economic Zone polygons display average year of range shifts within them. Warm colors are indicative of an early shift/high fishing revenue contribution from transboundary stocks while cold colors represent a late shift/low fishing revenue. EEZs with no distributional shift between 2006 and 2100 are represented in pale blue. B) Year of shared distribution shifts by UN sub-regions. Points color coded by the median year for all shifting stocks in the region. Horizontal dashed line represents the year by which countries have committed to reach full implementation of the 2030 Agenda. N = North, S = South, W = West and E = East. Ltn. Ame. and the Car. = Latin America and the Caribbean. Aus and New Z. = Australia and New Zealand.

###### Generate mean ToE across EEZs' stocks

```{r emergence_map_data, eval = F}
# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid,sau_fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
  ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  # filter(metric != "n_taxa") %>% 
  mutate(
    reverse = abs(value-2100)  + 2000
  )

@@

###### Plot ToE map

```{r emergence_map_plot, eval = F}
# -------------------------- #
# Call plot for both tresholds
# -------------------------- #
tresh_list <- c("tresh_one","tresh_two")
for(i in 1:2){

@@

Note this chunk needs `emergence_map_plot` to be ran.

@@

# EEZ map
eez_map <- ggplot(toe_map_data) +
  geom_sf(aes(fill = value), # for 2000 to 2100),
          color =  "white",
          size = 0.1
  ) +
  geom_sf(data = grey_land, aes(),
          fill = "grey50", 
          color =  "white",
          size = 0.1) +
  geom_sf(data = no_toe_eez, aes(fill = as.numeric(value)),
          color =  "white",
          size = 0.1) +
  scale_fill_viridis("Average year of range shift",
                     limits = c(2000,2100),
                     breaks = seq(2000,2100,25),
                     labels = seq(2000,2100,25),
                     direction = -1,
                     na.value = "lightblue"
  ) +
  my_ggtheme_m(leg_pos = "bottom") +
  theme(legend.key.width = unit(3, "line")) +
  guides(
    fill=guide_colorbar(title.position="top", 
                        title.hjust =0.5)
  )

# Land Map
land_map <- ggplot() +
  geom_sf(data = World_map_part,
          aes(fill = participation-2000, 
              color = participation-2000),
          size = 0.1
  )  +
  geom_sf(data = no_toe_land, aes(fill = as.numeric(value),
                                  color = as.numeric(value)),
          size = 0.1) +
  scale_fill_viridis("Transboundary fish revenue (%)",
                     limits = c(0,100),
                     breaks = seq(0,100,25),
                     labels = seq(0,100,25),
                     direction = 1,
                     na.value = "lightblue",
                     option = "A"
  ) +
  scale_color_viridis("Transboundary fish revenue (%)",
                      limits = c(0,100),
                      breaks = seq(0,100,25),
                      labels = seq(0,100,25),
                      direction = 1,
                      na.value = "lightblue",
                      option = "A"
  ) +
  my_ggtheme_m(leg_pos = "bottom") +
  theme(legend.key.width = unit(3, "line")) +
  guides(
    fill=guide_colorbar(title.position="top",
                        title.hjust =0.5)
  )

@@

@@

##### Fig. 4 Mapping the time of emergence of Top stocks

@@

top_stocks_per_country <- Eme_Res %>% 
  rename(geo_region = un_sub_region) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,geo_region,tresh,taxon_key) %>% 
  summarise(n()) %>% 
  left_join(Sau_data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  filter(!is.na(variable)) %>% 
  group_by(sau_fishing_entity,geo_region,tresh,variable) %>% 
  # Select top 5 most valuable stocks
  top_n(5,value)

@@

#### Species level analysis

Supplemental box picture by habitat preference

@@

Dem_pel <- Eme_Res %>% 
  filter(tresh == selected_tresh,
         !is.na(un_sub_region)) %>% 
  left_join(Spp_env_pref) %>% 
  mutate(DemersPelag = ifelse(is.na(DemersPelag),"other",paste(DemersPelag)),
  un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and the Car.",paste(un_sub_region)))

@@

# ------------------- #
# Test normal assumptions 
# ------------------- #

hist(Stats_data$emerging_yr) # Positively skewed
qqnorm(Stats_data$emerging_yr) # not normally distributed
skewness(Stats_data$emerging_yr) #1.02
kurtosis(Stats_data$emerging_yr) #2.82

@@

# Multiple differences but Eastern Asia, Lat. Ame. Car. and Polynesia are the ones who differ the most (e.g. differ with more regions).

@@

##  Stock Share Ratio Analysis

@@

#### Prepare data

```{r ssr_map_data, eval = T, echo = T}
# A function that makes a dateframe per connection (we will use these connections to plot each lines)
data_for_connection=function( dep_lon, dep_lat, arr_lon, arr_lat, group){
  inter <- gcIntermediate(c(dep_lon, dep_lat), c(arr_lon, arr_lat), n=50, addStartEnd=TRUE, breakAtDateLine=F)             
  inter=data.frame(inter)
  inter$group=NA
  diff_of_lon=abs(dep_lon) + abs(arr_lon)
  if(diff_of_lon > 180){
    inter$group[ which(inter$lon>=0)]=paste(group, "A",sep="")
    inter$group[ which(inter$lon<0)]=paste(group, "B",sep="")
  }else{
    inter$group=group
  }
  return(inter)
}

# Use a different palet between SSR and ToE
pal <- wesanderson::wes_palette("Zissou1",100,type = "continuous")

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na()

# Get paths data
path_data <- Data %>% 
  filter(
    variable %in% c("mean_eez")
  )

@@

for(i in c(1:nrow(path_data))){
  tmp=data_for_connection(path_data$start_lon[i], path_data$start_lat[i], path_data$end_lon[i], path_data$end_lat[i] , i)
  tmp$per_early_plot=path_data$per_early_plot[i]
  tmp$per_mid_plot=path_data$per_mid_plot[i]
  tmp$source=path_data$source[i]
  tmp$objective=path_data$target[i]
  data_ready_plot=rbind(data_ready_plot,tmp)
}

@@

#### Select a time step

```{r}
# SELECT A TIME STEP
# time_toplot <- "per_mid"
time_toplot <- "per_early"
```

#### Get data ready for time step

```{r ssr_map_data, eval = T, echo = T}

@@

# Grey land
grey_land <- World_map %>% 
  filter(is.na(fishing_entity_id)) %>% 
  filter(!sovereignt %in% c("Antarctica"))
```

#### Plot SSR map

```{r ssr_map_plot, eval = T, echo = T}
# Plot
p <-
  ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,
          col = "white") +
  geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
  geom_sf(data = subset(sf_ready_plot, percentage >= 0), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = point_data, aes(), color = "grey90") +
  geom_path(data = subset(arrows_data, percentage >= 0),
            aes(X, Y,
                group = group,
                col = percentage
            ),
            size = 1,
            arrow = arrow(length = unit(0.01, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m(leg_pos = "bottom") +
  scale_color_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(sf_ready_plot$percentage,na.rm=T)),
                        breaks = seq(0,max(sf_ready_plot$percentage,na.rm=T),10),
                        labels = c(seq(0,max(sf_ready_plot$percentage-10,na.rm=T),10),">50")
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                       colours = pal,
                       limits = c(0,max(sf_ready_plot$percentage,na.rm=T)),
                       breaks = seq(0,max(sf_ready_plot$percentage,na.rm=T),10),
                       labels = c(seq(0,max(sf_ready_plot$percentage-10,na.rm=T),10),">50")
  ) + guides(
    color=guide_colorbar(title.position="top")
  ) +
  theme(legend.key.width = unit(4,"line"))

@@

#### Regional maps for supplements

Note that the following chunk needs `ssr_map_data` to work.

@@

## ------------------- ##
# Latin america Map
## ------------------- ##

lat_am_map <- ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,
          col = "white") +
  # geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
  geom_sf(data = subset(sf_ready_plot, percentage >= 0), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = point_data, aes(), color = "grey90") +
  geom_path(data = subset(arrows_data, percentage >= 0),
            aes(X, Y,
                group = group,
                col = percentage
            ),
            size = 1,
            arrow = arrow(length = unit(0.03, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-9000000,-5000000),ylim = c(1000000, 4000000)) + 
  labs(x = "", y = "") +
  # scale_x_continuous(breaks = seq(-100,60,10)) +
  # scale_y_continuous(breaks = seq(10,30,10)) +
  my_ggtheme_m(leg_pos = "bottom") +
  theme(
    panel.background = element_rect(fill = "white", color = "white"),
    panel.grid.major =  element_line(color = "white")
  ) +
  scale_color_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(Lat_am_data$percentage)),
                        breaks = seq(0,max(Lat_am_data$percentage),10)
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                       colours = pal,
                       limits = c(0,max(Lat_am_data$percentage)),
                       breaks = seq(0,max(Lat_am_data$percentage),10)
  ) + guides(
    color=guide_colorbar(title.position="top", 
                         title.hjust =0.5)
  ) +
  theme(legend.key.width = unit(4,"line"))

@@

## ------------------- ##
# Northern Europe Map
## ------------------- ##

EU_map <- ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,
          col = "white") +
  geom_sf(data = subset(sf_ready_plot, percentage >= 0), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = point_data, aes(), color = "grey90") +
  geom_path(data = subset(arrows_data, percentage >= 0),
            aes(X, Y,
                group = group,
                col = percentage
            ),
            size = 1,
            arrow = arrow(length = unit(0.03, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-1300000,2000000),ylim = c(5500000, 7500000))  +
  labs(x = "", y = "") +
  scale_x_continuous(breaks = seq(-100,60,10)) +
  scale_y_continuous(breaks = seq(10,30,10)) +
  my_ggtheme_m(leg_pos = "bottom") +
  theme(
    panel.background = element_rect(fill = "white", color = "white"),
    panel.grid.major =  element_line(color = "white")
  ) +
  scale_color_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(EU_data$percentage)),
                        breaks = seq(0,max(EU_data$percentage),10)
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                       colours = pal,
                       limits = c(0,max(EU_data$percentage)),
                       breaks = seq(0,max(EU_data$percentage),10)
  ) + guides(
    color=guide_colorbar(title.position="top",
                         title.hjust =0.5)
  ) +
  theme(legend.key.width = unit(4,"line"))

@@

#### SSR TOP 5 figure

@@

top_taxon_list <-  unique(top_stocks_per_country$taxon_key)
# Read proportion results
suppressMessages(
  top_prop_results <- PropChange(top_taxon_list, links="y",top = T) %>%
    filter(!is.na(eez_neighbour)) %>%
    mutate(per_mid_plot =ifelse(per_mid >= 100, 100,
                                ifelse(per_mid <= -100,-100,per_mid)
    ),
    per_early_plot =ifelse(per_early >= 100, 100,
                           ifelse(per_early <= -100,-100,per_early)
    )
    )
)

@@

# Prepare data from results
top_data <- top_prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  # gather("variable","value",per_early:per_early_plot) %>% 
  filter(variable %in% c("mean_eez"))

top_data_ready_plot=data.frame()

for(i in c(1:nrow(top_data))){
  tmp=data_for_connection(top_data$start_lon[i], top_data$start_lat[i], top_data$end_lon[i], top_data$end_lat[i] , i)
  tmp$per_early_plot=top_data$per_early_plot[i]
  tmp$per_mid_plot=top_data$per_mid_plot[i]
  tmp$source=top_data$source[i]
  tmp$objective=top_data$target[i]
  top_data_ready_plot=rbind(top_data_ready_plot,tmp)
}

top_data_ready_plot <- top_data_ready_plot %>% 
  mutate(
    per_early = ifelse(per_early_plot >= 50,50,per_early_plot),
    per_mid = ifelse(per_mid_plot >= 50,50,per_mid_plot)) %>% 
  gather("time_step","percentage",per_early,per_mid)

top_sf_ready_plot <- top_data_ready_plot %>% 
  filter(time_step == "per_early") %>% 
  st_as_sf(coords = c("lon", "lat")) %>% 
  st_set_crs(4326) %>% # to match shapefiles
  st_transform(crs = "+proj=eck4")

# Get arrow data
top_arrows_data <- as.data.frame(st_coordinates(st_cast(top_sf_ready_plot,"POINT")$geometry)) %>% 
  bind_cols(top_data_ready_plot %>% 
              filter(time_step == "per_early")
  )
